Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-09-07 sections/approach.tex
very minor fixes

\subsection{Approach}
We seek to develop a model based on similarity criteria to classify (i.e. \emph{determine}) comments as either useful or useless. 
Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is determined to be \emph{most likely useful}, and for some degree of dissimilarity it is \emph{most likely useless}. Because this is a liklihood model, it is possible that a classification cannot be determined (i.e. no classification is likely enough) or determined to be in multiple classifications (i.e. overlap in likelihood conditions). It's important to keep in mind that these last two outcomes are not actual classifications whose interpretation is difficult and perhaps unreliable.     
The key to our approach is to determine the classification conditions in a practical, assurable manner that also is effective to use for assessing comment usefulness.

@@

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM)% \cite{wiki:vdm}
with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language. The Euclidian distance, which is a well-established measure of dissimilarity,  applies here analogously for retrieving irrelevant documents.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

The model is a form of \emph{supervised classification}% \cite{wiki:supervised}
where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g. likelihood that a comment is useful given its similarity is greater than some threshold value.    
The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the training data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \footnote{\url{http://en.wikipedia.org/w/index.php?title=F1_score&oldid=608940880}},
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.

>>>>

\subsection{Approach}
We seek to develop a model based on similarity criteria to classify (i.e. \emph{determine}) comments as either useful or useless. 
Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
That is, for some degree of similarity a comment is determined to be \emph{most likely useful}, and for some degree of dissimilarity it is \emph{most likely useless}. Because this is a likelihood model, it is possible that a classification cannot be determined (i.e. no classification is likely enough) or determined to be in multiple classifications (i.e. overlap in likelihood conditions). It is important to keep in mind that these last two outcomes are not actual classifications whose interpretation is difficult and perhaps unreliable.     
The key to our approach is to determine the classification conditions in a practical, assurable manner that also is effective to use for assessing comment usefulness.

@@

% again, I can't see Fig. \ref{fig:overview}(a)
% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
We calculate semantic similarity using the Vector Space Model (VSM) % \cite{wiki:vdm}
with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language. The Euclidian distance, which is a well-established measure of dissimilarity,  applies here analogously for retrieving irrelevant documents.
%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig. \ref{fig:overview}(b). \thai{The %overview figure does not have (a) and (b)...}
%\dan{what was the actual effort (in person-hours) to create the training data?}

The model is a form of \emph{supervised classification} % \cite{wiki:supervised}
where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g. likelihood that a comment is useful given its similarity is greater than some threshold value.    
The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the training data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ from useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \footnote{\url{http://en.wikipedia.org/w/index.php?title=F1_score&oldid=608940880}},
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.
